\documentclass{exam}
\usepackage{amssymb}
\usepackage{amsmath}
\title{CS113/DISCRETE MATHEMATICS-SPRING 2024}
\author{Problem Set 1}
\date{}

\begin{document}
\maketitle



\vspace{5mm}


\begin{questions}


\question . In an Island there are two kinds of inhabitants, knights, who always tell the truth, and knaves, who always lie. You encounter two people A and B. Determine, if possible, what A and B are if they address you in the ways described. 
\newline
(a) A says “At least one of us is a knave” and B says nothing.
\newline
(b) A says “The two of us are both knights” and B says “A is a knave”.
\newline
 (c) A says “I am a knave or B is a knight” and B says nothing. 
 \newline
(d) Both A and B say “I am a knight.”
\newline
 (e) A says “We are both knaves” and B says nothing.



\question Three friends are hanging out at a Cafe. The server approaches them and ask “Who wants a slice of cake?” The first friend says “I don’t know”. The second friend says “I don’t know”. Finally, the third friend says “No, not everyone wants cake”. The server comes back and gives slices of cake to the friends who want. 
\newline
How did the server figure out who wanted the cake?
\question
An ancient Sicilian legend says that the barber in a remote town who can be reached only by traveling a dangerous mountain road shaves those people, and only those people, who do not shave themselves. Can there be such a barber?

\question 
A father tells his two children, a boy and a girl, to play in their backyard without getting dirty. However, while playing, both children get mud on their foreheads. When the children stop playing, the father says “At least one of you has a muddy forehead,” and then asks the children to answer “Yes” or “No” to the question: “Do you know whether you have a muddy forehead?” The father asks this question twice. What will the children answer each time this question is asked, assuming that a child can see whether his or her sibling has a muddy forehead, but cannot see his or her own forehead? Assume that both children are honest and that the children answer each question simultaneously.
\question
Steve would like to determine the relative salaries of three coworkers using two facts. First, he knows that if Fred is not the highest paid of the three, then Janice is. Second, he knows that if Janice is not the lowest paid, then Maggie is paid the most. Is it possible to determine the relative salaries of Fred, Maggie, and Janice from what Steve knows? If so, who is paid the most and who the least? Explain your reasoning.
\question
Analyze the statement, “if you get more doubles than any other player you will lose, or that if you lose you must have bought the most properties,” using truth tables.

\end{questions}
\end{document}